LSOA domestic Electricty and Gas maps

### 2021-09-06 LSOA domestic Elec and Gas.Rmd
fixed free to be just y axis

# or without colour but using facets for Local Authorities
# first with fixed scales
ggplot(solent_elec, aes(x = as.factor(IMD_Decile), # forces a box plot at each value 
                   y =mean_de_diff, 
                   group = IMD_Decile)) +
  geom_boxplot() +
  labs(x = "IMD Decile",
       y = "Change in mean domestic kWh per meter",
       caption = "Electricity 2010-2019, all Solent LSOAs") +
  facet_wrap(la_name ~ .)

# now with 'free' scales
ggplot(solent_elec, aes(x = as.factor(IMD_Decile), # forces a box plot at each value 
                   y =mean_de_diff, 
                   group = IMD_Decile)) +
  geom_boxplot() +
  labs(x = "IMD Decile",
       y = "Change in mean domestic kWh per meter",
       caption = "Electricity 2010-2019, all Solent LSOAs") +
  facet_wrap(la_name ~ . , scales = "free")

@@

# or without colour but using facets for Local Authorities
# first with fixed scales
ggplot(solent_gas, aes(x = as.factor(IMD_Decile), # forces a box plot at each value 
                   y =dg_diff, 
                   group = IMD_Decile)) +
  geom_boxplot() +
  labs(x = "IMD Decile",
       y = "Change in mean domestic kWh per meter",
       caption = "Gas 2010-2019, all Solent LSOAs") +
  facet_wrap(la_name ~ .)

# now with 'free' scales to see pattern in each LA
ggplot(solent_gas, aes(x = as.factor(IMD_Decile), # forces a box plot at each value 
                   y =dg_diff, 
                   group = IMD_Decile)) +
  geom_boxplot() +
  labs(x = "IMD Decile",
       y = "Change in mean domestic kWh per meter",
       caption = "Gas 2010-2019, all Solent LSOAs") +
  facet_wrap(la_name ~ ., scales = "free")

>>>>

# or without colour but using facets for Local Authorities
# first with fixed scales
ggplot(solent_elec, aes(x = as.factor(IMD_Decile), # forces a box plot at each value 
                   y =mean_de_diff, 
                   group = IMD_Decile)) +
  geom_boxplot() +
  labs(x = "IMD Decile",
       y = "Change in mean domestic kWh per meter",
       caption = "Electricity 2010-2019, all Solent LSOAs") +
  facet_wrap(la_name ~ .)
```

Figure \@ref(fig:freeScaleElecIMD)

```{r freeScaleElecIMD, fig.cap = "freeScaleElecIMD"}
# now with 'free' scales
ggplot(solent_elec, aes(x = as.factor(IMD_Decile), # forces a box plot at each value 
                   y =mean_de_diff, 
                   group = IMD_Decile)) +
  geom_boxplot() +
  labs(x = "IMD Decile",
       y = "Change in mean domestic kWh per meter",
       caption = "Electricity 2010-2019, all Solent LSOAs") +
  facet_wrap(la_name ~ . , scales = "free_y")

@@

# or without colour but using facets for Local Authorities
# first with fixed scales
ggplot(solent_gas, aes(x = as.factor(IMD_Decile), # forces a box plot at each value 
                   y =dg_diff, 
                   group = IMD_Decile)) +
  geom_boxplot() +
  labs(x = "IMD Decile",
       y = "Change in mean domestic kWh per meter",
       caption = "Gas 2010-2019, all Solent LSOAs") +
  facet_wrap(la_name ~ .)
```

Figure \@ref(fig:freeScaleGasIMD)

```{r freeScaleGasIMD, fig.cap = "freeScaleGasIMD"}
# now with 'free' scales to see pattern in each LA
ggplot(solent_gas, aes(x = as.factor(IMD_Decile), # forces a box plot at each value 
                   y =dg_diff, 
                   group = IMD_Decile)) +
  geom_boxplot() +
  labs(x = "IMD Decile",
       y = "Change in mean domestic kWh per meter",
       caption = "Gas 2010-2019, all Solent LSOAs") +
  facet_wrap(la_name ~ ., scales = "free_y")
